---
title: "assignment2"
author: "CINDY BOSUBEN"
date: '2022-06-20'
output: html_document
---

```{r, echo = True}
#This dataset is about thnksgiving for the year 2015,it is sored in a database. It was colllected through a survey called monkeypoll survey where 1058 respondents. It was used to answer here is what Americans eat during thanksgiving 

```{r setup, include = true}
library(dplyr)
library(knitr)
library(dplyr)
```

```{r get data, include = TRUE}
#using read.csv to read data from csv file from a URL, 
url <- "thanksgiving-2015/thanksgiving-2015-poll-data.csv"
Example<- read.csv(url)
glimpse(Example)
```

```{r clean data, include = TRUE}
arrange(Example, freq)
``

`````` #This next chunk is inline code
This dataframe has `r nrow(Example)` ` rows and `r ncol(Example) columns. The names of the columns and a brief description of each are in the table below:
```{r}
#this makes a new data.frame called text_tbl with two columns, Names and Description
```{r, echo = True}
text_tbl <- data.frame( 
Names = c("ID”, “celebration”)
Description = c("RespondentID”, “Do you celebrate Thanksgiving") 
)
text_tbl #prints the table
```

```{r, echo = True}
data_pick3 <- select(Example, What kind of stuffing/dressing do you typically have, What type of cranberry saucedo you typically have, Do you typically have gravy).
Summarytable<-summary(data_pick3)#creates the summary
Summarytable #prints the summary in your output

```



